Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-04-29 paper/author_disambiguation.tex
double quotes

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig-pub-to-signature.pdf}
\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication.}
\label{fig:signature}
\end{figure*}

@@

\begin{enumerate}
  \item There are different
  ways of writing an author name, or signatures contain a typo
  (\eg, "Mueller, R." and "Muller, R.").

  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, "Martinez Torres, A." and "Torres, A. Martinez").

  \item An author has multiple surnames and, on some signatures, only the first surname is
  present (\eg, "Smith-Jones, A." and "Smith, A.")

  \item An author has multiple given names and they are not always all recorded (\eg,
  "Smith, Jack" and "Smith, A. J.")

@@

To account for these issues we propose instead to block signatures based on the
phonetic representation of the normalized surname.
Normalization involves stripping accents (\eg, "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
$\rightarrow$ "Waals, J. D."), while phonetization is based either on the
Double Metaphone \cite{doublemetaphone}, the NYSIIS \cite{nysiis} or the
Soundex \cite{Soundex} phonetic algorithms for mapping author names to their pronunciations.
Together, these processing steps allow for grouping of most name variants of the same
person in the same block with a small increase in the overall computational complexity, thereby solving case 1.

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig-pub-to-signature.pdf}
\caption{An example signature $s$ for ``Doe, John". A \textit{signature} is
defined as unique piece of information identifying an author on a publication,
along with any other metadata that can be derived from it, such as publication
title, co-authors or date of publication.}
\label{fig:signature}
\end{figure*}

@@

\begin{enumerate}
  \item There are different
  ways of writing an author name, or signatures contain a typo
  (\eg, ``Mueller, R." and ``Muller, R.").

  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, ``Martinez Torres, A." and ``Torres, A. Martinez").

  \item An author has multiple surnames and, on some signatures, only the first surname is
  present (\eg, ``Smith-Jones, A." and ``Smith, A.")

  \item An author has multiple given names and they are not always all recorded (\eg,
  ``Smith, Jack" and ``Smith, A. J.")

@@

To account for these issues we propose instead to block signatures based on the
phonetic representation of the normalized surname.
Normalization involves stripping accents (\eg, ``Jab\l{}o\'nski, \L{}" $\rightarrow$ ``Jablonski, L") and name
affixes that inconsistently appear in signatures (\eg, ``van der Waals, J. D."
$\rightarrow$ ``Waals, J. D."), while phonetization is based either on the
Double Metaphone \cite{doublemetaphone}, the NYSIIS \cite{nysiis} or the
Soundex \cite{Soundex} phonetic algorithms for mapping author names to their pronunciations.
Together, these processing steps allow for grouping of most name variants of the same
person in the same block with a small increase in the overall computational complexity, thereby solving case 1.
